A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
working on architecture

An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:

\medskip \noindent \textbf{Crawler}: This module deals with interacting with social media websites to collect information. For this project we will be collecting data from Twitter using Twitter Streaming APIs. We collected tweets from [xxxx] users. To collect this set of users we started with a set of 5 users and used snowball sampling to collect more users. We then used used the ``follow'' parameter of the filter method from Streaming API to generate a data stream for crowd detection.

\medskip \noindent \textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. This is the central module that detects crowds of different types - communication, content, geo-graphical, etc. In this project we will be discovering crowds based on communication only. The algorithm to discover crowds is described in Section~\ref{sec:crowd_algorithm}. Once crowds are discovered, this module formats crowds to a well defined crowds object and adds it to a DBMS.

\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework. It can appear both before and after the grouper module depending upon its funcationality. In the figure we have showed the module appear before grouper only. When the module appears before the grouper, it is used to weed out information unnecessary for the grouper. For example in case of crowd detection, it remove information like spam messages. When the module appears after the grouper, it cleans the data generated by the grouper. For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees. The module can also have additional functions that support features like search.

>>>>

An architecture for our solution is shown in Figure 1.  Data flows from a
crawler, through zero or more filters, to a grouper, and then through zero or
more filters, and then it is finally stored in a MongoDB database.  The various
modules of this architecture are as follows:

\subsection{Crawler}
Crawlers interact with social media websites to collect information. All of the
crawlers we use in this project acquire tweets and users from Twitter using
their APIs.

\medskip \noindent \textbf{Localcrawl}: This crawler collects data from users
in a region using the standard Twitter API. We started with a tiny sample set
of seed users. It uses snowball sampling to collect more users that are likely
to live in an area. Once we have a list of users

We have used this crawler and the crowd detection algorithms on both Bryan/College
Station and the Houston area, but the demo is currently exclusively running on the
Bryan/College Station data.

\medskip \noindent \textbf{GeoStream}: This crawler listens to Twitter's
streaming API to find geo-located tweets.  It recieves every geo-located tweet
posted from anywhere in the world.  In the future, this data may be used to
show crowds on a map.

\subsection{Grouper}
Groupers detect crowds in the data collected by a crawler.  The precise
definition of a crowd depends on the implementation of the grouper.  A grouper
could create crowds based on comunication patterns, geographical proximity, or
textual similarity. Once crowds are discovered, this module formats crowds to a
well defined crowds object and adds it to a DBMS.

\medskip \noindent \textbf{Mentions}:
For this project, we exclusivly discover crowds based on communtion.

...

The grouper module analyses the data
collected, to determine crowds and adds them to the DBMS. This is the central
module that detects crowds of different types - communication, content,
geo-graphical, etc. In this project we will be discovering crowds based on
communication only. The algorithm to discover crowds is described in
Section~\ref{sec:crowd_algorithm}.

\subsection{Filter}
Filters are used to remove unnecessary data and 
\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary
data from the framework. It can appear both before and after the grouper module
depending upon its funcationality. In the figure we have showed the module
appear before grouper only. When the module appears before the grouper, it is
used to weed out information unnecessary for the grouper. For example in case
of crowd detection, it remove information like spam messages. When the module
appears after the grouper, it cleans the data generated by the grouper. For,
example in case of crowd detection, it analyzes crowds discovered by the
grouper and removes un-necessary crowds, or crowds that don't meet specific
quality guarentees. The module can also have additional functions that support
features like search.
